MSc Project - Modelling a Double-Barred Galaxy as a Double Binary

### 2017-08-20 workspace/DoubleBars/MScProjectDoubleBarsv2.tex
Temp

\documentclass[a4paper,12pt]{article}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{float}
\usepackage{natbib}
\usepackage{listings}
\usepackage[skip=0pt]{caption}
\graphicspath{{./}}
\DeclareGraphicsExtensions{.eps}
%\setlength\abovecaptionskip{-5pt}
\author{Howard Kinsman}
\title{MSc Project - Modelling a Double-Barred Galaxy as a Double Binary}
\begin{document}
\maketitle
\begin{abstract}
TODO
\end{abstract}
\section{Introduction}
\subsection{Double-Barred Galaxies} 
Double-barred galaxies, where a smaller inner bar is nested inside a larger outer bar, were first observed in 1975 by de Vaucouleurs \citep{vaucouleurs}, however it was only in the 1990s that double-barred galaxies
were recognised as being a distinct category of galaxies. The current estimates of double-barred galaxy frequencies are $\approx30\%$ of barred galaxies and $\approx20\%$ of all galaxies \citep{erwin3}.
\cite{erwin2} surveyed 38 barred galaxies and found a total of 10 double-barred galaxies with no preference for Hubble type. They found that inner bars were about 12\% the size of the outer bars with
semi-major axes from $\approx250$pc to 1 kpc. Secondary bars probably rotate independently of, but in the same direction as their associated primary bars \cite{erwin2}.
\cite{erwin1} believe that innder bars probably rotate independently of their outer bars and suggest that they are relatively long-lived strucutures.
Inner bar size has been found to correlate slightly with outer bar size \citep{erwin3}. The median size ratio is $\approx0.12$ with an upper limit of $\approx0.25$ which is consistent with the theory that
inner bars cannot be too large without disrupting the orbit of the outer bar.

@@

Through the use of computer modeeling \cite{saha} showed that double bars can form without gas in a dark matter dominated halo. They produced a model where the inner bar was rotating at almost as slowly as the 
outer bar. The route to the formation of double bars maybe very different to that of a single bar.
%\citep{moiseev}, \citep{sellwood}

\subsection{N-Body Simulations and the Four-Body Problem}
Studies of three or more bodies interacting gravitationally dates back to the time of Newton. However it is only with the widespread use of computers that orbits of more than three bodies have been extensively studied. Today
N-body simulations are an essential tool in the study of solar system dynamics and galactic dynamics. The orbit-integration problems we have to address
vary in complexity from following a single particle in a given, smooth galactic potential, to tens of thousands of interacting stars in a globular cluster, to billions of dark-matter particles in a 
simulation of cosmological clustering \citep{binney}. Celestial mechanics during the preceding centuries has mainly focussed on the three body problem
due to the complexities involved in adding more bodies. It is estimated that within the Milky Way approximately two thirds of all stars exist in binary systems and a further one fifth of these are in triple systems whilst a
further fifth still exist in systems with more than three bodies \citep{steves}. \cite{steves} estimate that $\approx2\times10^9$ quadruple systems exist in the Milky Way galaxy. They found that quadruple systems exist in two
forms: a double binary or linear.

The classical equations of motion for an N-body problem are:
\begin{equation}
m_i\mathbf{\ddot{r}}=\sum_{i\neq{j}}\frac{{m_i}{m_j}}{r^3_{ij}}\mathbf{r_{ij}}
\qquad
i=1,2,3...
\end{equation}
where $\mathbf{r_i}=\left(x_i,y_i\right)$ and $\mathbf{r_{ij}}=\mathbf{r_j}-\mathbf{r_i}$. 
The units have been selected so that the gravitational constant (G) is equal to one. In simulations it is natural to choose units where G = 1 and the units of length nand mass are conventionally chosen
so that the total mass of the system is M = 1 \citep{heggie}.

The four body problem, specifically, has been studied extensively by \cite{steves}. Here they model four equal mass bodies orbiting in circular coplanar orbits. This model they term the Caledonian problem, because
their research is being carried out at Glasgow Caledonian University.
Approximately a century ago the Copenhagen problem was studied extensively in Copenhagen which consisted of a three body problem: two equal mass bodies and an infinitesimally small test particle. \cite{szell} also
studied the Caledonian problem and found that the stability of the system is dependent upon a constant termed the Szebehely constant. The Caledonian Symmetric Double Binary Problem (CSDBP) is relevant in 
studying the stability and evolution of symmetric quadruple stellar clusters and exoplanetary systems of two planets orbiting a binary pair of stars \citep{alvarez}.

Methods for the study of N-body simulations have changed considerably since the advent of computers. In a study of N-body simulations \cite{trenti} mentions a pioneering attempt by Holmberg in 1941 which used 
light bulbs and galvanometers to track the evolution of 37 particles. However it wasn't until the early seventies and the advent of computers that this field really got started. 
Nowadays simulations can up to a million particles \citep{heggie} which is of particular relevance to the study of globular
clusters. I refer the reader to \cite{aarseth} for much more detailed explanation of the field of N-body simulations.
 %\citep{collins}, \citep{moulton}

@@

\cite{garzon} studied the dynamical evolution of two isolated bars, within the same galaxy, under their mutual gravitational interaction. They considered two cases purely analytically: rotation of rigid bodies and
rotation of deformable rotation. They found that the bars oscillate in size according to the relative angle between the bars. This is broadly in agreement with \citep{debattista}.
What follows is an attempt to verify the calculations in \citep{garzon} but using a simpler model of a double-barred galaxy using a double binary.
 %\citep{du2}, \citep{macie1}, \citep{macie2},  \citep{macie4}
 %\citep{malhotra}, \citep{manos}, \citep{shen2}
\newpage
\section{Methods}
The model was created using OdeInt from Numerical Recipes \citep{press}. OdeInt was first converted to Fortran 90 for this purpose.
Fortran 90 was selected as the language of choice in order to avoid the fixed line limitations of Fortran 77.
OdeInt performs integration using the Runge-Kutta method. The Runge-Kutta method is an extension of the Euler method of solving differential equations. However the Euler method
is an example of first-order integration whilst Runge-Kutta is second and higher order and so is mcuh more accurate. The OdeInt uses a subroutine called RK4 which utilises fourth-order Runge-Kutta integration.
It also uses a technique known as adaptive stepsize. This involves adjusting the size of the integration steps to ensure the same level of accuracy however rapidly the function being integrated changes.
Many small steps should tiptoe through treacherous terrain, while a few great strides should speed through smooth uninteresting countryside \citep{press}.

For a four body problem, Equation 1 results in the following:

@@

These equations of motion are second-order ordinary differential equations (ODEs) but any second-oder ODE can be written as a system

@@

ODEs which leaves us with a total of sixteen simultanious first-order ODEs to solve.

@@

starting point. The inner binary had an initial neglible mass.

@@

I then proceeded to perturb the system by gradually increasing the mass of the inner binary. As the system became unstable I componensated for

@@

\newpage
\section{Results}
As can be seen from Fig. \ref{fig:config1} even a neglible mass inner binary causes the outer binary to begin to separate and become less tightly bound.
Figures Fig. \ref{fig:config1} to \ref{fig:config32i} show plots of the double binary using the parameters given in Table \ref{tab:variables}.
In many cases the inner binary is only visible as a point at the centre of the outer binary.
As the mass of the inner binary increased the system became increasingly unstable and the effect on the outer binary became more pronounced.
Even the `stable' configurations listed in Table \ref{tab:variables} hold for only a few orbits.

\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{./2016results/stablebase/Orbit.eps}
\caption{Configuration 1}
\label{fig:config1}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{./2016results/stablebase/Inner.eps}
\caption{Configuration 1 - Inner Bar}
\label{fig:config1i}
\end{figure}
\ref{fig:config1} and \ref{fig:config1i} show the inital orbits when the circular inner binary is placed within the outer binary.

\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{./2016results/002-5-001/Orbit.eps}
\caption{Configuration 2}
\label{fig:config2}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{./2016results/002-5-001/Inner.eps}
\caption{Configuration 2 - Inner Bar}
\label{fig:config2i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{./2016results/003-5-001/Orbit.eps}
\caption{Configuration 3}
\label{fig:config3}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{./2016results/003-5-001/Inner.eps}
\caption{Configuration 3 - Inner Bar}
\label{fig:config3i}
\end{figure}
\ref{fig:config2} to \ref{fig:config3i} show plots where just the mass of the inner binary has been gradually increased. Nothing else was changed.
By \ref{fig:config3i}, the inner binary can clearly be seen to be pulled apart by the gravitational affect of the outer binary.

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/004-5-004/Orbit.eps}
\caption{Configuration 4}
\label{fig:config4}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/004-5-004/Inner.eps}
\caption{Configuration 4 - Inner Bar}
\label{fig:config4i}
\end{figure}
To counteract the effect of the increased mass of the inner binary in \ref{fig:config4} and \ref{fig:config4i} the initial separation of the 
inner binary has been increased.

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/004-55-004/Orbit.eps}
\caption{Configuration 5}
\label{fig:config5}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/004-55-004/Inner.eps}
\caption{Configuration 5 - Inner Bar}
\label{fig:config5i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/004-57-004/Orbit.eps}
\caption{Configuration 6}
\label{fig:config6}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/004-57-004/Inner.eps}
\caption{Configuration 6 - Inner Bar}
\label{fig:config6i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/005-58-005-3/Orbit.eps}
\caption{Configuration 7}
\label{fig:config7}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/005-58-005-3/Inner.eps}
\caption{Configuration 7 - Inner Bar}
\label{fig:config7i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/005-58-005-4/Orbit.eps}
\caption{Configuration 8}
\label{fig:config8}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/005-58-005-4/Inner.eps}
\caption{Configuration 8 - Inner Bar}
\label{fig:config8i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/005-58-005-35/Orbit.eps}
\caption{Configuration 9}
\label{fig:config9}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/005-58-005-35/Inner.eps}
\caption{Configuration 9 - Inner Bar}
\label{fig:config9i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/006-6-006-3/Orbit.eps}
\caption{Configuration 10}
\label{fig:config10}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/006-6-006-3/Inner.eps}
\caption{Configuration 10 - Inner Bar}
\label{fig:config10i}
\end{figure}
In \ref{fig:config5} to \ref{fig:config10i} the initial velocity of the outer binary has also been gradually increased to also counteract the effect
of the increased mass of the inner binary. In order for these systems to be relatively stable the initial velocity of the inner binary was reduced. At this point 
both the inner and outer binaries had started to separate and become increasingly elliptical.

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/025-65-02/Orbit.eps}
\caption{Configuration 11}
\label{fig:config11}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/025-65-02/Inner.eps}
\caption{Configuration 11 - Inner Bar}
\label{fig:config11i}
\end{figure}
In order to bring the orbits back into approximate circularity it was necessary to again increase the velocity of the inner binary. This is illustrated
in \ref{fig:config11} and \ref{fig:config11i}. The mass of the inner binary has also increased considerably from the previous configurations.

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/025-7-025-5/Orbit.eps}
\caption{Configuration 12}
\label{fig:config12}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/025-7-025-5/Inner.eps}
\caption{Configuration 12 - Inner Bar}
\label{fig:config12i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/03-7-03-5/Orbit.eps}
\caption{Configuration 13}
\label{fig:config13}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/03-7-03-5/Inner.eps}
\caption{Configuration 13 - Inner Bar}
\label{fig:config13i}
\end{figure}

Figs. \ref{fig:config12} to \ref{fig:config13i} show the mass of the inner binary slowly increasing and adjustments made to both velocity of outer binary
and separation of inner binary.

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/035-75-04-4/Orbit.eps}
\caption{Configuration 14}
\label{fig:config14}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/035-75-04-4/Inner.eps}
\caption{Configuration 14 - Inner Bar}
\label{fig:config14i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/04-75-045-4/Orbit.eps}
\caption{Configuration 15}
\label{fig:config15}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/04-75-045-4/Inner.eps}
\caption{Configuration 15 - Inner Bar}
\label{fig:config15i}
\end{figure}

As the mass of the inner binary was increased, it became necessary to reduce the velocity of the inner binary, Figs. \ref{fig:config14} to \ref{fig:config15i}.

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/05-75-045-4/Orbit.eps}
\caption{Configuration 16}
\label{fig:config16}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/05-75-045-4/Inner.eps}
\caption{Configuration 16 - Inner Bar}
\label{fig:config16i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/05-75-05-35/Orbit.eps}
\caption{Configuration 17}
\label{fig:config17}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/05-75-05-35/Inner.eps}
\caption{Configuration 17 - Inner Bar}
\label{fig:config17i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/05-75-05-3/Orbit.eps}
\caption{Configuration 18}
\label{fig:config18}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/05-75-05-3/Inner.eps}
\caption{Configuration 18 - Inner Bar}
\label{fig:config18i}
\end{figure}

Holding the mass of the inner binary at .05 the system showed signs of more stability if the velocity of the inner binary was further reduced, Figs. \ref{fig:config16} to \ref{fig:config18i}.

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/06-8-06-25/Orbit.eps}
\caption{Configuration 19}
\label{fig:config19}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/06-8-06-25/Inner.eps}
\caption{Configuration 19 - Inner Bar}
\label{fig:config19i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/08-9-08-15/Orbit.eps}
\caption{Configuration 20}
\label{fig:config20}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/08-9-08-15/Inner.eps}
\caption{Configuration 20 - Inner Bar}
\label{fig:config20i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/09-95-09-1/Orbit.eps}
\caption{Configuration 21}
\label{fig:config21}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/09-95-09-1/Inner.eps}
\caption{Configuration 21 - Inner Bar}
\label{fig:config21i}
\end{figure}

Further reduction of the velocity of the inner binary allowed further increase of inner binary mass without losing stability, Figs. \ref{fig:config19} to \ref{fig:config21i}.

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{float}
\usepackage{natbib}
\usepackage{listings}
\usepackage[skip=0pt]{caption}
\graphicspath{{./}}
\DeclareGraphicsExtensions{.eps}
%\setlength\abovecaptionskip{-5pt}
\author{Howard Kinsman}
\title{MSc Project - Modelling a Double-Barred Galaxy as a Double Binary}
\begin{document}
\maketitle
\begin{abstract}
TODO
\end{abstract}
\section{Introduction}
\subsection{Double-Barred Galaxies} 
Double-barred galaxies, where a smaller inner bar is nested inside a larger outer bar, were first observed in 1975 by de Vaucouleurs \citep{vaucouleurs}, however it was only in the 1990s that double-barred galaxies
were recognised as being a distinct category of galaxies. The current estimates of double-barred galaxy frequencies are $\approx30\%$ of barred galaxies and $\approx20\%$ of all galaxies \citep{erwin3}.
\cite{erwin2} surveyed 38 barred galaxies and found a total of 10 double-barred galaxies with no preference for Hubble type. They found that inner bars were about 12\% the size of the outer bars with
semi-major axes from $\approx250$pc to 1 kpc. Secondary bars probably rotate independently of, but in the same direction as their associated primary bars \cite{erwin2}.
\cite{erwin1} believe that inner bars probably rotate independently of their outer bars and suggest that they are relatively long-lived structures.
Inner bar size has been found to correlate slightly with outer bar size \citep{erwin3}. The median size ratio is $\approx0.12$ with an upper limit of $\approx0.25$ which is consistent with the theory that
inner bars cannot be too large without disrupting the orbit of the outer bar.

@@

Through the use of computer modeling \cite{saha} showed that double bars can form without gas in a dark matter dominated halo. They produced a model where the inner bar was rotating at almost as slowly as the 
outer bar. The route to the formation of double bars maybe very different to that of a single bar.
%\citep{moiseev}

\subsection{N-Body Simulations and the Four-Body Problem}
Studies of three or more bodies interacting gravitationally dates back to the time of Newton. However, it is only with the widespread use of computers that orbits of more than three bodies have been extensively studied. Today
N-body simulations are an essential tool in the study of solar system dynamics and galactic dynamics. The orbit-integration problems we have to address
vary in complexity from following a single particle in a given, smooth galactic potential, to tens of thousands of interacting stars in a globular cluster, to billions of dark-matter particles in a 
simulation of cosmological clustering \citep{binney}. Celestial mechanics during the preceding centuries has mainly focused on the three-body problem
due to the complexities involved in adding more bodies. It is estimated that within the Milky Way approximately two thirds of all stars exist in binary systems and a further one fifth of these are in triple systems whilst a
further fifth still exist in systems with more than three bodies \citep{steves}. \cite{steves} estimate that $\approx2\times10^9$ quadruple systems exist in the Milky Way galaxy. They found that quadruple systems exist in two
forms: a double binary or linear.

The classical equations of motion for an N-body problem are:
\begin{equation}
m_i\mathbf{\ddot{r}}=\sum_{i\neq{j}}\frac{{m_i}{m_j}}{r^3_{ij}}\mathbf{r_{ij}}
\qquad
i=1,2,3...
\end{equation}
where $\mathbf{r_i}=\left(x_i,y_i\right)$ and $\mathbf{r_{ij}}=\mathbf{r_j}-\mathbf{r_i}$. 
The units have been selected so that the gravitational constant (G) is equal to one. In simulations, it is natural to choose units where G = 1 and the units of length and mass are conventionally chosen
so that the total mass of the system is M = 1 \citep{heggie}.

The four-body problem, specifically, has been studied extensively by \cite{steves}. Here they model four equal mass bodies orbiting in circular coplanar orbits. This model they term the Caledonian problem, because
their research is being carried out at Glasgow Caledonian University.
Approximately a century ago the Copenhagen problem was studied extensively in Copenhagen which consisted of a three-body problem: two equal mass bodies and an infinitesimally small test particle. \cite{szell} also
studied the Caledonian problem and found that the stability of the system is dependent upon a constant termed the Szebehely constant. The Caledonian Symmetric Double Binary Problem (CSDBP) is relevant in 
studying the stability and evolution of symmetric quadruple stellar clusters and exoplanetary systems of two planets orbiting a binary pair of stars \citep{alvarez}.

Methods for the study of N-body simulations have changed considerably since the advent of computers. In a study of N-body simulations \cite{trenti} mentions a pioneering attempt by Holmberg in 1941 which used 
light bulbs and galvanometers to track the evolution of 37 particles. However, it wasn't until the early seventies and the advent of computers that this field really got started. 
Nowadays simulations can up to a million particles \citep{heggie} which is of particular relevance to the study of globular
clusters. I refer the reader to \cite{aarseth} for much more detailed explanation of the field of N-body simulations.

@@

\cite{garzon} studied the dynamical evolution of two isolated bars, within the same galaxy, under their mutual gravitational interaction. They considered two cases purely analytically: rotation of rigid bodies and
rotation of deformable rotation. They found that the bars oscillate in size according to the relative angle between the bars. This is broadly in agreement with \citep{debattista}.
What follows is an attempt to verify the calculations in \citep{garzon} but using a simpler model of a double-barred galaxy using a double binary.

\newpage
\section{Methods}
The model was created using OdeInt from Numerical Recipes \citep{press}. OdeInt was first converted to Fortran 90 for this purpose.
Fortran 90 was selected as the language of choice in order to avoid the fixed line limitations of Fortran 77.
OdeInt performs integration using the Runge-Kutta method. The Runge-Kutta method is an extension of the Euler method of solving differential equations. However the Euler method
is an example of first-order integration whilst Runge-Kutta is second and higher order and so is much more accurate. The OdeInt uses a subroutine called RK4 which utilizes fourth-order Runge-Kutta integration.
It also uses a technique known as adaptive stepsize. This involves adjusting the size of the integration steps to ensure the same level of accuracy however rapidly the function being integrated changes.
Many small steps should tiptoe through treacherous terrain, while a few great strides should speed through smooth uninteresting countryside \citep{press}.

For a four-body problem, Equation 1 results in the following:

@@

These equations of motion are second-order ordinary differential equations (ODEs) but any second-order ODE can be written as a system

@@

ODEs which leaves us with a total of sixteen simultaneous first-order ODEs to solve.

@@

starting point. The inner binary had an initial negligible mass.

@@

I then proceeded to perturb the system by gradually increasing the mass of the inner binary. As the system became unstable I compensated for

@@

\clearpage
\section{Results}
As can be seen from Fig. \ref{fig:config1} even a negligible mass inner binary causes the outer binary to begin to separate and become less tightly bound.
Figures Fig. \ref{fig:config1} to \ref{fig:config32i} show plots of the double binary using the parameters given in Table \ref{tab:variables}.
As the mass of the inner binary increased the system became increasingly unstable and the effect on the outer binary became more pronounced.
Even the `stable' configurations listed in Table \ref{tab:variables} hold for only a few orbits.
Figs. \ref{fig:config1} and \ref{fig:config1i} show the initial orbits when the circular inner binary is placed within the outer binary. The placement of
the inner binary can clearly be seen to affect the orbit of the outer binary even though the inner binary mass is very low.
\includegraphics[width=.9\textwidth]{./2016results/stablebase/Orbit.eps}
\caption{Configuration 1}
\label{fig:config1}
\includegraphics[width=.9\textwidth]{./2016results/stablebase/Inner.eps}
\caption{Configuration 1 - Inner Bar}
\label{fig:config1i}

Figs. \ref{fig:config2} to \ref{fig:config3i} show plots where just the mass of the inner binary has been gradually increased. Nothing else was changed.
By Fig. \ref{fig:config3i}, the inner binary has been pulled apart by the gravitational affect of the outer binary.
\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{./2016results/002-5-001/Orbit.eps}
\caption{Configuration 2}
\label{fig:config2}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{./2016results/002-5-001/Inner.eps}
\caption{Configuration 2 - Inner Bar}
\label{fig:config2i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{./2016results/003-5-001/Orbit.eps}
\caption{Configuration 3}
\label{fig:config3}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{./2016results/003-5-001/Inner.eps}
\caption{Configuration 3 - Inner Bar}
\label{fig:config3i}
\end{figure}

To counteract the effect of the increased mass of the inner binary in Figs. \ref{fig:config4} and \ref{fig:config4i} the initial separation of the 
inner binary has been increased. This has a noticeable stabilizing effect on the inner binary which has regained approximate circularity.
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/004-5-004/Orbit.eps}
\caption{Configuration 4}
\label{fig:config4}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/004-5-004/Inner.eps}
\caption{Configuration 4 - Inner Bar}
\label{fig:config4i}
\end{figure}

In figs. \ref{fig:config5} to \ref{fig:config10i} the initial velocity of the outer binary has also been gradually increased to also counteract the effect
of the increased mass of the inner binary. In order for these systems to be relatively stable the initial velocity of the inner binary was reduced. At this point 
both the inner and outer binaries had started to separate and the inner binary became increasingly elliptical.
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/004-55-004/Orbit.eps}
\caption{Configuration 5}
\label{fig:config5}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/004-55-004/Inner.eps}
\caption{Configuration 5 - Inner Bar}
\label{fig:config5i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/004-57-004/Orbit.eps}
\caption{Configuration 6}
\label{fig:config6}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/004-57-004/Inner.eps}
\caption{Configuration 6 - Inner Bar}
\label{fig:config6i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/005-58-005-3/Orbit.eps}
\caption{Configuration 7}
\label{fig:config7}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/005-58-005-3/Inner.eps}
\caption{Configuration 7 - Inner Bar}
\label{fig:config7i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/005-58-005-4/Orbit.eps}
\caption{Configuration 8}
\label{fig:config8}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/005-58-005-4/Inner.eps}
\caption{Configuration 8 - Inner Bar}
\label{fig:config8i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/005-58-005-35/Orbit.eps}
\caption{Configuration 9}
\label{fig:config9}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/005-58-005-35/Inner.eps}
\caption{Configuration 9 - Inner Bar}
\label{fig:config9i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/006-6-006-3/Orbit.eps}
\caption{Configuration 10}
\label{fig:config10}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/006-6-006-3/Inner.eps}
\caption{Configuration 10 - Inner Bar}
\label{fig:config10i}
\end{figure}

In order to bring the orbits back into approximate circularity it was necessary to again increase the velocity of the inner binary. This is illustrated
in Figs. \ref{fig:config11} and \ref{fig:config11i}. The mass of the inner binary has also increased considerably from the previous configurations.
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/025-65-02/Orbit.eps}
\caption{Configuration 11}
\label{fig:config11}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2016results/025-65-02/Inner.eps}
\caption{Configuration 11 - Inner Bar}
\label{fig:config11i}
\end{figure}

Figs. \ref{fig:config12} to \ref{fig:config13i} show the mass of the inner binary being slowly increased with adjustments made to both velocity of outer binary
and separation of inner binary.
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/025-7-025-5/Orbit.eps}
\caption{Configuration 12}
\label{fig:config12}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/025-7-025-5/Inner.eps}
\caption{Configuration 12 - Inner Bar}
\label{fig:config12i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/03-7-03-5/Orbit.eps}
\caption{Configuration 13}
\label{fig:config13}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/03-7-03-5/Inner.eps}
\caption{Configuration 13 - Inner Bar}
\label{fig:config13i}
\end{figure}

As the mass of the inner binary was increased, it became necessary to reduce the velocity of the inner binary, Figs. \ref{fig:config14} to \ref{fig:config15i}.
However, the inner binary was showing signs of increasingly chaotic orbits.
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/035-75-04-4/Orbit.eps}
\caption{Configuration 14}
\label{fig:config14}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/035-75-04-4/Inner.eps}
\caption{Configuration 14 - Inner Bar}
\label{fig:config14i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/04-75-045-4/Orbit.eps}
\caption{Configuration 15}
\label{fig:config15}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/04-75-045-4/Inner.eps}
\caption{Configuration 15 - Inner Bar}
\label{fig:config15i}
\end{figure}

Whilst holding the mass of the inner binary at .05, the system showed signs of more stability if the velocity of the inner binary was further reduced, Figs. \ref{fig:config16} to \ref{fig:config18i}.
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/05-75-045-4/Orbit.eps}
\caption{Configuration 16}
\label{fig:config16}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/05-75-045-4/Inner.eps}
\caption{Configuration 16 - Inner Bar}
\label{fig:config16i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/05-75-05-35/Orbit.eps}
\caption{Configuration 17}
\label{fig:config17}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/05-75-05-35/Inner.eps}
\caption{Configuration 17 - Inner Bar}
\label{fig:config17i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/05-75-05-3/Orbit.eps}
\caption{Configuration 18}
\label{fig:config18}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/05-75-05-3/Inner.eps}
\caption{Configuration 18 - Inner Bar}
\label{fig:config18i}
\end{figure}

Further reduction of the velocity of the inner binary allowed further increase of inner binary mass without losing stability, Figs. \ref{fig:config19} to \ref{fig:config21i}. The simulation is
now stable enough for the outer binary to complete one orbit and proceed with a second.
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/06-8-06-25/Orbit.eps}
\caption{Configuration 19}
\label{fig:config19}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/06-8-06-25/Inner.eps}
\caption{Configuration 19 - Inner Bar}
\label{fig:config19i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/08-9-08-15/Orbit.eps}
\caption{Configuration 20}
\label{fig:config20}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/08-9-08-15/Inner.eps}
\caption{Configuration 20 - Inner Bar}
\label{fig:config20i}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/09-95-09-1/Orbit.eps}
\caption{Configuration 21}
\label{fig:config21}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{./2017results/09-95-09-1/Inner.eps}
\caption{Configuration 21 - Inner Bar}
\label{fig:config21i}
\end{figure}
